Estimating duration in the presence of misclassification

### 2024-07-31 cis-imperfect-testing.tex
Rob second p109 comment (on definitions)

Introducing false negatives means that $O(j)$, the observation vector of episode $j$, is now random, even if $B_j$ and $E_j$ are known.
Therefore, the results between the tests that bound episode $j$'s beginning and end times should now enter into the likelihood.
For tractability, I consider only tests between the negative tests providing an upper bound on the length of episode $j$.

To formalise this, I define analogous variables to those in \cref{E-perf-test:sec:posterior}.
To start with, define the relevant testing times for any episode $j$ with $O(j) = \vec{\nu}_k$ as $\sched'_k = \{ t \in \sched_{i_k} \ssep r_k^{(b)} \leq t \leq r_k^{(e)} + 1 \}$ and let $m_k$ denote the size of this set.
Denote the elements of $\sched'_k$ by $t_{k,1} < \dots < t_{k,m_k}$.
Let $\set{E}' = \{ \vec{\nu}_1', \dots, \vec{\nu}_{N_E'}' \}$ be a new set of possible observations of detected episodes, including the pattern of positive and negative tests.
Represent the observations such that for any $\vec{\nu}_k' \in \set{E}'$, $\vec{\nu}_k' = [\vec{\nu}_{k}, \vec{y}_k]^T$, where $\vec{y}_k \in \{ 0, 1 \}^{m_k}$ with $y_{k,l}$ being the test result at time $t_{k,l}$.

The elements of $\set{E}'$ are all $\vec{\nu}_k'$ such that:
\begin{enumerate}
  \item $\vec{\nu}_k \in \set{E}$.
  \item The elements of $\vec{y}_k$ corresponding to the tests at times $r_k^{(b)}$ and $l_k^{(e)}$ are positive, \ie $y_{k,1} = y_{k,m_k-1} = 1$.
  \item The element of $\vec{y}_k$ corresponding to the test at time $r_k^{(e)} + 1$ is negative, \ie $y_{k,m_k} = 0$.
\end{enumerate}
The final two conditions are due to the construction of the intervals as positive and negative tests bounding the beginning and end times of the episode.

Let $O'(j)$ be the observations generated by episode $j$ including the new vector of results.
As before, $O'(j) \in \set{E}'$ indicates that episode $j$ was detected; otherwise, $O'(j) = \emptyset$.

Similarly, let $p_k'$, $p_{ik}'$, $p_u'$, and $p_{iu}'$ have the same definition as $p_k$, $p_{ik}$, $p_u$, and $p_{iu}$ respectively except replacing $O$ with $O'$ and $\vec{\nu}_k$ with $\vec{\nu}_k'$, and conditioning on $\psens$.
As before, $p'_k = 1/\Ncis p'_{ik}$ and $p'_u = 1/\Ncis \sum_{i=1}^{\Ncis} p'_{iu}$.

>>>>

Introducing false negatives means that $O(j)$, containing the relevant information for episode $j$, is now random, even if $B_j$ and $E_j$ are known.
Therefore, the results between the tests that bound episode $j$'s beginning and end times should now enter into the likelihood.
For tractability, I consider only tests between the negative tests providing an upper bound on the length of episode $j$.

To do so, define a random vector $O'(j)$ with state space $\{\emptyset\} \cup \set{E}'$ which will replace $O(j)$ from \cref{E-perf-test}.
As before, $O'(j) = \emptyset$ if episode $j$ is undetected.
Otherwise, $O'(j) \in \set{E}'$ where $\set{E}' = \{ \vec{\nu}_1', \dots, \vec{\nu}_{N_E'}' \}$ augments the space $\set{E}$ with test results during the episode.
The elements of $\set{E}'$ are all $\vec{\nu}_k' = [\vec{\nu}_k, \vec{y}_k]^T$ where $\vec{\nu}_k \in \set{E}$ and $\vec{y}_k$ is a vector of test results for the relevant testing times, $\sched'_k = \{ t \in \sched_{i_k} \ssep r_k^{(b)} \leq t \leq r_k^{(e)} + 1 \}$.
To formalise the definition of $\vec{y}_k$, let $m_k$ denote the size of $\sched'_k$ and denote the elements of $\sched'_k$ by $t_{k,1} < \dots < t_{k,m_k}$.
Then, $\vec{y}_k \in \{0, 1\}^{m_k}$ and satisfies the following two conditions.
\begin{enumerate}
  \item The elements of $\vec{y}_k$ corresponding to the tests at times $r_k^{(b)}$ and $l_k^{(e)}$ are positive, \ie $y_{k,1} = y_{k,m_k-1} = 1$.
  \item The element of $\vec{y}_k$ corresponding to the test at time $r_k^{(e)} + 1$ is negative, \ie $y_{k,m_k} = 0$.
\end{enumerate}
These conditions are due to the construction of the intervals as positive and negative tests bounding the beginning and end times of the episode.

Let $p_k'$, $p_{ik}'$, $p_u'$, and $p_{iu}'$ have the same definition as $p_k$, $p_{ik}$, $p_u$, and $p_{iu}$ respectively except replacing $O$ with $O'$ and $\vec{\nu}_k$ with $\vec{\nu}_k'$, and conditioning on $\psens$.
As before, $p'_k = 1/\Ncis p'_{ik}$ and $p'_u = 1/\Ncis \sum_{i=1}^{\Ncis} p'_{iu}$.
